---
title: "Nordic Model analysis: TALIS 2024"
author: "Blinded"
date: "`r Sys.Date()`"
output: html_document
---

- Lundberg et al., 2020 - local explanations using SHAP - with figures and examlpes of how to show
- Yang et al., 2023 - shows 9 different ways of doing weights in bayesian analyses.
- MacNell et al., 2023 - argues for the importance of sampling weights in regressions; for large data sets, you can simply weight results. and run models unweighted.
- Lundberg & Lee, 2017 - SHAP
- Oh et al., 2026 - guidelines for using machine learning in complex surveys. not useful... 

```{r setup, include=FALSE}
# setwd("m:/NordicModel/code/NordicModel")
options(future.globals.maxSize = 6000 * 1024^2)
require(dbarts)
require(bartMan )
require(tidyverse)
require(ggplot2)
require(survey)
require(coda)
knitr::opts_chunk$set(cache.lazy=FALSE, echo=T, warnings=F)
filter <- dplyr::filter
select <- dplyr::select
require(haven)
require(arm)
require(tinytex)
require(haven)
require(labelled)
library(bartXViz)
source("FixedExtractTrees.r")

options(ggplot2.discrete.colour = see::okabeito_colors(c("light blue","amber","green","orange","red") ) %>% unname ) 
options(ggplot2.discrete.fill   = see::okabeito_colors(c("light blue","amber","green","orange","red") ) %>% unname ) 

paste. <- function(...) paste(... , sep=".")
hist.rug <- function(TheVar, IDnames = NULL, ylim=NULL, breaks="Sturges", ...,
                     main=paste("Var=",deparse(substitute(TheVar))), describe=T) {
  if (describe) try(print(psych::describe(TheVar)))
  par(cex.lab = 1, cex.axis = 1.2, lwd = 2)
  suppressWarnings(HistData <- hist(TheVar, plot=F,breaks=breaks, ... ))
  if (is.null(ylim))
    HistData = hist(TheVar, ylim=c(0, max(HistData$counts)*1.2),breaks=breaks, main=main,... )
  else
    HistData = hist(TheVar,breaks=breaks, main=main, ... )
  rug(TheVar, col = "red")
  if (any(class(TheVar)=="Date")) {
    DensityData = density(na.omit(TheVar))
  } else DensityData = density(as.numeric(na.omit(TheVar)))
  lines(DensityData$x, DensityData$y * (max(HistData$counts)/max(DensityData$y)), col = "blue")
  mtext(sprintf("M: %.2f\nSD: %.2f",mean(TheVar,na.rm=TRUE),sd(TheVar,na.rm=TRUE)),side=3, line=-2,adj = 1)

  if (!is.null(IDnames)) identify(TheVar, rep(0, length(TheVar)), labels = IDnames)
}
unFactor  <- function(x) return(if (is.factor(x)) as.numeric(levels(x)[x]) else x )
CutForReg <- function(x,num) cut(x,UniqueQuant(x,num),include.lowest=TRUE)
UniqueQuant <- function(x, n=10) unique(quantile(x,0:n/n,na.rm=TRUE,type=1)) # Helper in other functions around regressions
```

```{r loading, include=FALSE}
load(file.path("..","..","data","btgintt4.RData"))

BTGINTT4 <- BTGINTT4 %>% 
  select(-(IDCNTRY:IDCNTPOP),-(IDTQUEST:ITMODE_TQ),-(IDPOP:IEADATE),-(TT4G01:TT4G08),-TT4G11,-contains("TT4G47"),
         -contains("TT4G13"),-contains("TT4G16"),-contains("TT4G21"),-contains("TT4G23"),-contains("TT4G24"),-TT4G48A,
         -contains("TT4G25"),-contains("TT4G35"),-TT4G36,-contains("TT4G37"),-contains("TT4G38"),-(TT4G39A:TT4G45) ,
         -(TT4G59A:TT4G59F),-contains("TT4G62"),-contains("TT4G63"), -(TT4G73A:TT4G76D), -(TT4G82A:TT4G84),
         -T4TAGEGR,-T4THEDAT,-T4TYQUAL,-T4TEMPWH,-T4CLSINF,-T4FASPR,-T4TNSCH,-T4TYEXPTS,-T4TYEXPTT,-T4TYEXPE,
         -T4TYEXPO,-T4TCSIZE,-T4TLANG,-T4TLANGN,-contains("TT4G20"),-TT4G22,TCHWGT
         ) %>% 
  mutate(across(c(starts_with("TT4"),-TT4G49 ), to_factor )) %>%
  select_if( function(x) any(!is.na(x)) ) %>%
  mutate(TT4G09=case_when(grepl("Permanent",TT4G09)~1,!grepl("Permanent",TT4G09)~0),
         TT4G12=case_when(grepl("Full-time",TT4G12)~1,grepl("71-90",TT4G12)~0.8,
                          grepl("50-70",TT4G12)~0.6,grepl("less than 50",TT4G12)~0.25) ) %>% 
  mutate(across(c(starts_with("T4") ), function(x) ifelse(x>9000,NA,unFactor(x))  ) ) %>% 
  mutate(UseDigRes =data.frame(T4DRTIIA,T4DRTWCI) %>% rowMeans(na.rm=T) ,
         Leadership=data.frame(T4INSTLE,T4RELEAD) %>% rowMeans(na.rm=T) ) %>% 
  select(IDSCHOOL,IDTEACH,CNTRY,T4EXINF,T4COLES,T4SELF,T4SEMUL,T4GROMST,T4SESEN,T4COMSEL,T4SEDRT,T4BLFDRT,T4ADVDRT,T4CLAIN,T4COGAC,T4CLASM,T4PDGENP,T4EMPS,
         T4CLSDIS,T4ADLE,T4PBLE,T4AUTCH,T4FULFIL,T4OPPART,T4SESDEV,T4TLEAD,T4STUD,T4CLIBUL,T4STUHAR,T4CHFAT,T4MOPU,T4MOSU,T4WELS,T4WLOADT,T4STBEH,T4JSENVT,
         T4JSPROT,T4VALP,T4JOYTCH,T4DRTIIA,T4DRTWCI,T4INSTLE,T4RELEAD,UseDigRes,Leadership,TCHWGT) %>% 
  mutate( # Set all missing values to an extreme case, which lets the bart model easily isolate those cases in prediction model 
    across( T4EXINF:Leadership , function(x) ifelse(is.na(x), 0, x ) ) ) %>% 
  mutate(Nordic=ifelse(CNTRY %in% c("DNK","NOR","SWE","FIN","ISL") , 1,0)  )
```

Create training and test data

```{r CreateTrainingTest}
set.seed(1312)

CountrySizes <- BTGINTT4 %>% 
  count(CNTRY) %>% 
  mutate(Nover=n-4000) %>% 
  mutate( # select all over 4000 or 10%, whichever is bigger to be test data. this limits training data size for large countries, which was suggested by a reviewer
    Ntrain=ifelse(Nover/n <= 0.1, as.integer(n*0.1) , Nover)) %>% 
  select(-Nover,-n)

BTGINTT4 %>%
  count(CNTRY,IDSCHOOL) %>% 
  merge(CountrySizes) %>% 
  mutate(train=0) %>% 
  group_by(CNTRY) %>% 
  group_modify(~{
    while ( sum(.x$train) < .x$Ntrain[1] ) {
      a <- sample(1:nrow(.x),1)
      .x[a, "train"] <- .x[a,"n"]
    }
    .x
  } ) %>% 
  as.data.frame %>% 
  filter(train>0) %>% 
  with( paste.(CNTRY,IDSCHOOL) ) ->
  TestSchools

Test <- BTGINTT4 %>% filter(paste.(CNTRY,IDSCHOOL) %in% TestSchools )
BTGINTT4 <- BTGINTT4 %>% filter(!( paste.(CNTRY,IDSCHOOL) %in% TestSchools ) )
```

# Correlations

There are some scales that are correlated over 0.79. We combine these scales to ensure that high collinearity does not impact our ability to explore variable importance.

Scale1   Scale2   Correlation
-------- -------- ------------
T4DRTIIA T4DRTWCI   0.8067
T4INSTLE T4RELEAD   0.7988

```{r correlationsbetweenScales, cache=T}
BTGINTT4 %>% select(T4EXINF,T4COLES,T4SELF,T4SEMUL,T4GROMST,T4SESEN,T4COMSEL,T4SEDRT,T4BLFDRT,T4ADVDRT,T4CLAIN,T4COGAC,T4CLASM,T4PDGENP,T4EMPS,T4CLSDIS,T4ADLE,T4PBLE,T4AUTCH,T4FULFIL,T4OPPART,T4SESDEV,T4TLEAD,T4STUD,T4CLIBUL,T4STUHAR,T4CHFAT,T4MOPU,T4MOSU,T4WELS,T4WLOADT,T4STBEH,T4JSENVT,T4JSPROT,T4VALP,T4JOYTCH,UseDigRes,Leadership) %>% cor(use="pair") %>% gplots::heatmap.2(trace="none",cexCol=.7,cexRow=.7,margins=c(8,8), dendrogram="both" )
```


# Test for ICCs

```{r exploreICC, cache=T}
iccs <- misty::multilevel.icc(BTGINTT4 %>% select(T4EXINF,T4COLES,T4SELF,T4SEMUL,T4GROMST,T4SESEN,T4COMSEL,T4SEDRT,T4BLFDRT,T4ADVDRT,T4CLAIN,T4COGAC,T4CLASM,T4PDGENP,T4EMPS,T4CLSDIS,T4ADLE,T4PBLE,T4AUTCH,T4FULFIL,T4OPPART,T4SESDEV,T4TLEAD,T4STUD,T4CLIBUL,T4STUHAR,T4CHFAT,T4MOPU,T4MOSU,T4WELS,T4WLOADT,T4STBEH,T4JSENVT,T4JSPROT,T4VALP,T4JOYTCH,CNTRY,UseDigRes,Leadership,IDSCHOOL) %>% mutate_all(function(x) ifelse(x==0,NA,x)) ,
                      cluster = c( "CNTRY" , "IDSCHOOL" ),
                      type="1a")
iccs %>% t %>% knitr::kable(caption="Table of percentages of variation in variables that is between schools",digits=2)

hist.rug(iccs["CNTRY",],main="Distribution of variance\nat the country level\n across variables")
hist.rug(iccs["IDSCHOOL",],main="Distribution of variance\nat the school level\n across variables")
```

# BART Model

## run model 

The CV model to verify ideal parameters is not run due to the amount of time it takes to run.

```{r runCV, cache=T, eval=F}
model_cv <- xbart(Nordic~ T4EXINF+T4COLES+T4SELF+T4SEMUL+T4GROMST+T4SESEN+T4COMSEL+T4SEDRT+T4BLFDRT+T4ADVDRT+T4CLAIN+T4COGAC+T4CLASM+T4PDGENP+T4EMPS+T4CLSDIS+T4ADLE+T4PBLE+T4AUTCH+T4FULFIL+T4OPPART+T4SESDEV+T4TLEAD+T4STUD+T4CLIBUL+T4STUHAR+T4CHFAT+T4MOPU+T4MOSU+T4WELS+T4WLOADT+T4STBEH+T4JSENVT+T4JSPROT+T4VALP+T4JOYTCH+UseDigRes+Leadership,
  data = BTGINTT4,n.burn = c(20000,1000,1000), n.samples=2000, 
  method="k-fold",n.test=5,n.reps=10,  
  n.trees = c(50,100,200),
  k=c(1.5, 2.0),
  power=c(1.5,2),
  base=c(0.95,0.99),
  loss = "log",     
  n.threads = 20,
  seed=1121
)

apply(model_cv,c(2,3,4),mean)
```

```{r runmodelpiece, eval=F}
library(dbarts)

control <- dbartsControl(
  n.trees = 50,
  n.burn = 20000, n.cuts=50,
  n.samples = 5000, n.thin = 10, printEvery =200,
  n.chains = 8, n.threads = 8,
  keepTrees = TRUE, k=1.5, 
  updateState = TRUE
)

sampler <- dbarts(BTGINTT4 %>% select(T4EXINF,T4COLES,T4SELF,T4SEMUL,T4GROMST,T4SESEN,T4COMSEL,T4SEDRT,T4BLFDRT,T4ADVDRT,T4CLAIN,T4COGAC,T4CLASM,T4PDGENP,T4EMPS,T4CLSDIS,T4ADLE,T4PBLE,T4AUTCH,T4FULFIL,T4OPPART,T4SESDEV,T4TLEAD,T4STUD,T4CLIBUL,T4STUHAR,T4CHFAT,T4MOPU,T4MOSU,T4WELS,T4WLOADT,T4STBEH,T4JSENVT,T4JSPROT,T4VALP,T4JOYTCH,UseDigRes,Leadership) %>% as.matrix,
                  factor(BTGINTT4$Nordic),
                  control = control,
                  tree.prior = cgm(power=2, base=0.99)
                  )

initial_results <- sampler$run(numBurnIn = 20000, numSamples = 2000)

macro_predictions <- split( plogis(initial_results$yhat.train) %>% apply(c(1), mean) %>% t ,
                            rep(1:initial_results$call$nchain , each=initial_results$call$ndpost/initial_results$call$keepevery) )

mcmc_chains <- lapply(1:length(macro_predictions), function(i) {
  mcmc(macro_predictions[[i]])
}) %>%  as.mcmc.list

gelman.diag(mcmc_chains)
plot(mcmc_chains)
print(coda::effectiveSize(mcmc_chains))
# 4. Add more iterations later 
# This resumes directly from the last state of the previous run
additional_results <- sampler$run(numBurnIn = 0, numSamples = 2000)


```

```{r runmodel2, cache=F}
X = BTGINTT4 %>% select(T4EXINF,T4COLES,T4SELF,T4SEMUL,T4GROMST,T4SESEN,T4COMSEL,T4SEDRT,T4BLFDRT,T4ADVDRT,T4CLAIN,T4COGAC,T4CLASM,T4PDGENP,T4EMPS,T4CLSDIS,T4ADLE,T4PBLE,T4AUTCH,T4FULFIL,T4OPPART,T4SESDEV,T4TLEAD,T4STUD,T4CLIBUL,T4STUHAR,T4CHFAT,T4MOPU,T4MOSU,T4WELS,T4WLOADT,T4STBEH,T4JSENVT,T4JSPROT,T4VALP,T4JOYTCH,UseDigRes,Leadership) %>% as.matrix

model <- bart(
  x.train = as.matrix(X),
  y.train = factor(BTGINTT4$Nordic),
  ntree = 50, power=2, base=0.99, k=1.5,
  # nskip = 20000, ndpost =30000, keepevery = 300,
  nskip = 50000, ndpost = 20000, keepevery = 100,
  nchain = 8, nthread = 8,
  seed=561,
  keeptrees = TRUE
)

# model2 <- bart2(
#   formula = Nordic ~ .,
#   data = cbind(Nordic = as.numeric(BTGINTT4$Nordic), as.data.frame(X)),
#   n.trees = 50, power=2, base=0.99, k=1.5,
#   n.burn = 250, n.samples = 500, n.thin = 5,
#   n.chains = 8, n.threads = 8, 
#   seed=591,
#   keepTrees = TRUE
# )
```

```{r codeconverge2, cache=T,eval=T}
macro_predictions <- split( plogis(model$yhat.train) %>% apply(c(1), mean) %>% t ,
                            rep(1:model$call$nchain , each=model$call$ndpost/model$call$keepevery) )

mcmc_chains <- lapply(1:length(macro_predictions), function(i) {
  mcmc(macro_predictions[[i]])
}) %>%  as.mcmc.list

gelman.diag(mcmc_chains)
print(coda::effectiveSize(mcmc_chains))
plot(mcmc_chains)

```

```{r codeconverge11, cache=T,eval=T,fig.height=20}
var_counts <- model$varcount 

var_counts_list <- split(as.data.frame(var_counts) ,rep(1:model$call$nchain,each=model$call$ndpost/model$call$keepevery) )
var1_mcmc <- as.mcmc.list(lapply(1:length(var_counts_list), function(i) mcmc(var_counts_list[[i]])))
# Check convergence on feature assignment
gelman.diag(var1_mcmc)
plot(var1_mcmc)
```


## Variable selection and variable importance

Figure below shows that student harassment is by far the most important variable, followed by fulfillment of lesson aims, beliefs in digital resources (positive), student-teacher relationship, use of digital tools for individual instruction, autonomy in teaching, and exchange of information among teachers.

### BartXViz

```{r variableImportance31, cache=T}
pfun <- function (object, newdata) {
  predict(object , newdata)
}

shap_results <- Explain(model, 
          X = as.data.frame(X), 
          newdata = Test %>% select(T4EXINF,T4COLES,T4SELF,T4SEMUL,T4GROMST,T4SESEN,T4COMSEL,T4SEDRT,T4BLFDRT,T4ADVDRT,T4CLAIN,T4COGAC,T4CLASM,T4PDGENP,T4EMPS,T4CLSDIS,T4ADLE,T4PBLE,T4AUTCH,T4FULFIL,T4OPPART,T4SESDEV,T4TLEAD,T4STUD,T4CLIBUL,T4STUHAR,T4CHFAT,T4MOPU,T4MOSU,T4WELS,T4WLOADT,T4STBEH,T4JSENVT,T4JSPROT,T4VALP,T4JOYTCH,UseDigRes,Leadership) %>% as.data.frame, 
          pred_wrapper = pfun)
```

###  Plot SHAP - averaged across observations 

```{r plotShap1, cache=T}
# shap_results$phis <- lapply(shap_results$phis, function(x) { dim(x) <- c(length(x),1); return(x) } )
plot(shap_results,average="obs",title="obs")
```

###  Plot SHAP - averaged across post

```{r plotShap2, cache=T}
plot(shap_results,average="post",title="post")
```

```{r customshapplot}
shap_results$phis %>% 
  lapply( function(x) colMeans(abs(x)) ) %>% 
  lapply( function(x) data.frame(m   =mean(x),
                                 q10=quantile(x,0.10) ,
                                 q80=quantile(x,0.80) ) ) %>% 
  bind_rows(.id="Var") -> phi_CI

phi_CI %>% arrange(m) %>% 
  mutate(Var=factor(Var,unique(Var)) ) %>% 
  ggplot(aes(x=Var,y=m,ymin=q10,ymax=q80)) +
    geom_point()+
    geom_text(aes(label=round(m,3)),position=position_nudge(0.48,0.002),size=3 )+
    geom_pointrange()+
    theme_bw() +
    coord_flip(xlim=c(1,38.3))+
    labs(x="",y="SHAP values")
ggsave(file="customshapresults.png",height=14,width=14,units="cm")
```

###  Plot separate post SHAP

```{r plotShap6,cache=T}
# 1. Duplicate your main SHAP object for the TRUE group
shap_nordic_true <- shap_results
# Filter the SHAP values (phis) and the row predictions (fx)
shap_nordic_true$phis <- lapply(shap_results$phis, function(x) x[Test$Nordic==1,, drop = FALSE])
shap_nordic_true$newdata <- shap_nordic_true$newdata[Test$Nordic==1,, drop = FALSE]
shap_nordic_true$fx   <- shap_results$fx[Test$Nordic == 1]

# 2. Duplicate your main SHAP object for the FALSE group
shap_nordic_false <- shap_results
shap_nordic_false$phis <- lapply(shap_results$phis, function(x) x[Test$Nordic==0,, drop = FALSE])
shap_nordic_false$newdata <- shap_nordic_false$newdata[Test$Nordic==0,, drop = FALSE]
shap_nordic_false$fx   <- shap_results$fx[Test$Nordic == 0]

plot(shap_nordic_true,  average = "post", title= "Post Graph: Nordic Countries")
plot(shap_nordic_false, average = "post", title= "Post Graph: Non-Nordic Countries")
```

### Shap plots

```{r sthar}
SHAPtable <- Test %>% 
  select(IDTEACH,CNTRY,Nordic,T4STUHAR,T4BLFDRT,T4ADLE,T4STUD,Leadership,T4EXINF,T4CHFAT,T4CLIBUL,T4OPPART,T4FULFIL) %>% 
  mutate(T4STUHAR_Shap  =shap_results$phis$T4STUHAR   %>% apply(1,mean,na.rm=T),
         T4BLFDRT_Shap  =shap_results$phis$T4BLFDRT   %>% apply(1,mean,na.rm=T),
         T4ADLE_Shap    =shap_results$phis$T4ADLE     %>% apply(1,mean,na.rm=T),
         T4STUD_Shap    =shap_results$phis$T4STUD     %>% apply(1,mean,na.rm=T),
         Leadership_Shap=shap_results$phis$Leadership %>% apply(1,mean,na.rm=T),
         T4EXINF_Shap   =shap_results$phis$T4EXINF    %>% apply(1,mean,na.rm=T),
         T4CHFAT_Shap   =shap_results$phis$T4CHFAT    %>% apply(1,mean,na.rm=T),
         T4CLIBUL_Shap  =shap_results$phis$T4CLIBUL   %>% apply(1,mean,na.rm=T),
         Nordic=ifelse(Nordic==1,"Nordic","Non-Nordic")
  )
```

```{r}
SHAPtable %>% 
  filter(T4STUHAR!=0) %>% 
  ggplot(aes(x=T4STUHAR,color=Nordic,y=T4STUHAR_Shap)) +
    geom_point(alpha=0.2,shape=4)+geom_smooth()

SHAPtable %>% 
  filter(T4BLFDRT!=0) %>% 
  ggplot(aes(x=T4BLFDRT,color=Nordic,y=T4BLFDRT_Shap)) +
    geom_point(alpha=0.2,shape=4)+geom_smooth()

SHAPtable %>% 
  filter(T4ADLE!=0) %>% 
  ggplot(aes(x=T4ADLE,color=Nordic,y=T4ADLE_Shap)) +
    geom_point(alpha=0.2,shape=4)+geom_smooth()

SHAPtable %>% 
  filter(T4STUD!=0) %>% 
  ggplot(aes(x=T4STUD,color=Nordic,y=T4STUD_Shap)) +
    geom_point(alpha=0.2,shape=4)+geom_smooth()

SHAPtable %>% 
  filter(Leadership!=0) %>% 
  ggplot(aes(x=Leadership,color=Nordic,y=Leadership_Shap)) +
    geom_point(alpha=0.2,shape=4)+geom_smooth()

SHAPtable %>% 
  filter(T4EXINF!=0) %>% 
  ggplot(aes(x=T4EXINF,color=Nordic,y=T4EXINF_Shap)) +
    geom_point(alpha=0.2,shape=4)+geom_smooth()
```

```{r}
require(ggridges)
SHAPtable %>% 
  filter(T4STUHAR!=0) %>% 
  group_by(CNTRY) %>% 
  mutate(m=mean(T4STUHAR,na.rm=T)) %>% 
  ungroup %>% 
  mutate(CNTRY=factor(CNTRY,unique(CNTRY[order(m)])) ) %>% 
  ggplot(aes(x=T4STUHAR,fill=Nordic,y=CNTRY)) +
    geom_density_ridges()

SHAPtable %>% 
  filter(T4BLFDRT!=0) %>% 
  group_by(CNTRY) %>% 
  mutate(m=mean(T4BLFDRT,na.rm=T)) %>% 
  ungroup %>% 
  mutate(CNTRY=factor(CNTRY,unique(CNTRY[order(m)])) ) %>% 
  ggplot(aes(x=T4BLFDRT,fill=Nordic,y=CNTRY)) +
    geom_density_ridges()

SHAPtable %>% 
  filter(T4ADLE!=0) %>% 
  group_by(CNTRY) %>% 
  mutate(m=mean(T4ADLE,na.rm=T)) %>% 
  ungroup %>% 
  mutate(CNTRY=factor(CNTRY,unique(CNTRY[order(m)])) ) %>% 
  ggplot(aes(x=T4ADLE,fill=Nordic,y=CNTRY)) +
    geom_density_ridges()

SHAPtable %>% 
  filter(T4STUD!=0) %>% 
  group_by(CNTRY) %>% 
  mutate(m=mean(T4STUD,na.rm=T)) %>% 
  ungroup %>% 
  mutate(CNTRY=factor(CNTRY,unique(CNTRY[order(m)])) ) %>% 
  ggplot(aes(x=T4STUD,fill=Nordic,y=CNTRY)) +
    geom_density_ridges()

SHAPtable %>% 
  filter(Leadership!=0) %>% 
  group_by(CNTRY) %>% 
  mutate(m=mean(Leadership,na.rm=T)) %>% 
  ungroup %>% 
  mutate(CNTRY=factor(CNTRY,unique(CNTRY[order(m)])) ) %>% 
  ggplot(aes(x=Leadership,fill=Nordic,y=CNTRY)) +
    geom_density_ridges()

SHAPtable %>% 
  filter(T4EXINF!=0) %>% 
  group_by(CNTRY) %>% 
  mutate(m=mean(T4EXINF,na.rm=T)) %>% 
  ungroup %>% 
  mutate(CNTRY=factor(CNTRY,unique(CNTRY[order(m)])) ) %>% 
  ggplot(aes(x=T4EXINF,fill=Nordic,y=CNTRY)) +
    geom_density_ridges()
```



```{r}
SHAPtable %>% 
  filter(T4STUHAR!=0 & T4CHFAT!=0) %>% 
  mutate(T4CHFATc=CutForReg(T4CHFAT,3) ) %>% 
  ggplot(aes(x=T4STUHAR,y=T4STUHAR_Shap)) +
    geom_point( aes(color=T4CHFAT),position=position_jitter())+
    geom_smooth(aes(linetype=T4CHFATc),linewidth=1.5,se=F)+
    facet_wrap(~Nordic)+
    scale_color_viridis_c(option="magma")

SHAPtable %>% 
  filter(T4STUHAR!=0 & T4CHFAT!=0) %>% 
  mutate(T4STUHARc=CutForReg(T4STUHAR,3)) %>% 
  ggplot(aes(x=T4CHFAT,y=T4CHFAT_Shap)) +
    geom_point( aes(color=T4STUHAR),position=position_jitter(w=0.1))+
    geom_smooth(aes(linetype=T4STUHARc),linewidth=1.5,se=F)+
    facet_wrap(~Nordic)+
    scale_color_viridis_c(option="magma")
```


```{r}
SHAPtable %>% 
  filter(T4STUHAR!=0) %>% 
  mutate(T4STUDc=CutForReg(T4STUD,3) ) %>% 
  ggplot(aes(x=T4STUHAR,y=T4STUHAR_Shap)) +
    geom_point( aes(color=T4STUD),position=position_jitter(w=0.1))+
    geom_smooth(aes(linetype=T4STUDc),linewidth=1.5,se=F)+
    facet_wrap(~Nordic)+
    scale_color_viridis_c(option="magma")

SHAPtable %>% 
  filter(T4CHFAT!=0) %>% 
  mutate(T4STUHARc=CutForReg(T4STUHAR,3)) %>% 
  ggplot(aes(x=T4STUD,y=T4STUD_Shap)) +
    geom_point( aes(color=T4STUHAR),position=position_jitter(w=0.1))+
    geom_smooth(aes(linetype=T4STUHARc),linewidth=1.5,se=F)+
    facet_wrap(~Nordic)+
    scale_color_viridis_c(option="magma")
```

Based on Shap values

T4STUHAR x T4CHFAT


```{r}
SHAPtable %>% 
  filter(T4STUHAR!=0) %>% 
  mutate(T4CLIBULc=CutForReg(T4CLIBUL,4) ) %>% 
  ggplot(aes(x=T4STUHAR,y=T4STUHAR_Shap)) +
    geom_point( aes(color=T4CLIBUL),position=position_jitter(w=0.1))+
    geom_smooth(aes(linetype=T4CLIBULc),linewidth=1.5,se=F)+
    facet_wrap(~Nordic)+
    scale_color_viridis_c(option="magma")

SHAPtable %>% 
  filter(T4CLIBUL!=0) %>% 
  mutate(T4STUHARc=CutForReg(T4STUHAR,4)) %>% 
  ggplot(aes(x=T4CLIBUL,y=T4CLIBUL_Shap)) +
    geom_point( aes(color=T4STUHAR),position=position_jitter(w=0.1))+
    geom_smooth(aes(linetype=T4STUHARc),linewidth=1.5,se=F)+
    facet_wrap(~Nordic)+
    scale_color_viridis_c(option="magma")

```

 X STUHAR
T4FULFIL X T4OPPART x 



```{r}
SHAPtable %>% 
  filter(T4EXINF!=0) %>% 
  mutate(T4OPPARTc=CutForReg(T4OPPART,4) ) %>% 
  ggplot(aes(x=T4EXINF,y=T4EXINF_Shap)) +
    geom_point( aes(color=T4OPPART),shape=20,alpha=0.2)+
    geom_smooth(aes(fill=T4OPPARTc),linewidth=1.5,se=F)+
    facet_wrap(~Nordic)+
    scale_color_viridis_c(option="magma")
    

SHAPtable %>% 
  filter(T4EXINF!=0) %>% 
  mutate(T4FULFILc=CutForReg(T4FULFIL,4)) %>% 
  ggplot(aes(x=T4EXINF,y=T4EXINF_Shap)) +
    geom_point( aes(color=T4FULFIL),shape=20,alpha=0.2)+
    geom_smooth(aes(fill=T4FULFILc),linewidth=1.5,se=F)+
    facet_wrap(~Nordic)+
    scale_color_viridis_c(option="magma")

```

# Results

- T4STUHAR - Student harassment in school - higher is more nordic... 
- T4FULFIL - Fulfillment of lesson aims (complexity of teaching) - lower is more nordic.... 
- T4BLFDRT - Beliefs in digital resources and tools - lower is more nordic
- T4STUD - Teacher-student relations - higher is more nordic
- UseDigRes - Use of digital resources and tools combined individual and whole classs
- T4AUTCH - Autonomy of teaching
- T4EXINF - Exchange of information and ideas among teachers
- T4CLAIN - Clarity of instruction
- T4EMPS - Empathy with students
- T4OPPART - Opportunities to participate in school decisions
- T4SESDEV - Social and emotional skill development
- Leadership - leadership
- T4VALP - Perceptions of value and policy influence
- T4PDGENP - Need for professional development in general pedagogy
- T4CLSDIS - Perceived classroom disruption
- T4PBLE - Progression-based learning
- T4GROMST - Growth mindset
- T4SESEN - Self-efficacy in special education needs
- T4WELS - Workplace well-being and stress
- T4JSENVT - Job satisfaction with work environment
- T4TLEAD - Teacher leadership

```{r runModel6, cache=T}
predictedTrain <- predict(model, X)

predictedTest <- predict(model, Test %>% select(T4EXINF,T4COLES,T4SELF,T4SEMUL,T4GROMST,T4SESEN,T4COMSEL,T4SEDRT,T4BLFDRT,T4ADVDRT,T4CLAIN,T4COGAC,T4CLASM,T4PDGENP,T4EMPS,T4CLSDIS,T4ADLE,T4PBLE,T4AUTCH,T4FULFIL,T4OPPART,T4SESDEV,T4TLEAD,T4STUD,T4CLIBUL,T4STUHAR,T4CHFAT,T4MOPU,T4MOSU,T4WELS,T4WLOADT,T4STBEH,T4JSENVT,T4JSPROT,T4VALP,T4JOYTCH,UseDigRes,Leadership)   )

hist.rug(apply(predictedTrain,2,mean),main="Distribution of prediction in training data")
hist.rug(apply(predictedTest ,2,mean),main="Distribution of prediction in test data")

# BTGINTT4$predicted <- apply(predictedTrain,2,mean)
# Test$predicted <- apply(predictedTest ,2,mean)

save(BTGINTT4, Test,predictedTrain,predictedTest,shap_results,file="MainModelwithPredicted.rData")
```


## Association between sampling weights and predicted values

```{r assocWeightPredicted,eval=T}
BTGINTT4 %>% 
  group_by(CNTRY) %>% 
  mutate(TCHWGT=TCHWGT/median(TCHWGT)) %>% ungroup %>% 
  ggplot(aes(x=TCHWGT,color=CNTRY))+
    geom_density()+
    labs(title="Training Data")

BTGINTT4 %>% 
  mutate(predicted=apply(predictedTrain,2,mean)) %>% 
  filter(CNTRY %in% c("DNK","NOR","SWE","FIN","ISL")) %>% 
  group_by(CNTRY) %>% 
  mutate(TCHWGT=TCHWGT/median(TCHWGT)) %>% ungroup %>%  
  ggplot(aes(y=predicted,x=TCHWGT))+
    geom_smooth(se=T)+
    facet_wrap(~CNTRY,scales="free_x")
```

```{r assocWeightPredicted2,eval=T,fig.height=12,fig.width=12}
BTGINTT4 %>% 
  mutate(predicted=apply(predictedTrain,2,mean)) %>% 
  filter(!(CNTRY %in% c("DNK","NOR","SWE","FIN","ISL")) ) %>% 
  group_by(CNTRY) %>% 
  mutate(TCHWGT=TCHWGT/median(TCHWGT)) %>% ungroup %>%  
  ggplot(aes(y=predicted,x=TCHWGT))+
    geom_smooth(se=T)+
    facet_wrap(~CNTRY,scales="free_x")
```

## Print Prediction Tables Training Data

```{r rocit, cache=T}
library(ROCit)
ROCit_objTr <- rocit(score=apply(predictedTrain,2,mean),class=BTGINTT4$Nordic,negref =0)
str( ROCIT_NordicTr <- plot(ROCit_objTr))
ciROC(ROCit_objTr, method = "binomial") %>% plot(legend = TRUE)
ciAUC(ROCit_objTr, delong = TRUE)
save(ROCIT_NordicTr,ROCit_objTr,file="ROCIT_Nordic_Train.rData")
```


## Print Prediction Tables Test Data

```{r rocittest, cache=T}
ROCit_obj <- rocit(score=apply(predictedTest,2,mean) ,class=Test$Nordic,negref =0)
str( ROCIT_Nordic <- plot(ROCit_obj) )
ciROC(ROCit_obj, method = "binomial") %>% plot(legend = TRUE)
ciAUC(ROCit_obj, delong = TRUE)
save(ROCIT_Nordic,ROCit_obj,file="ROCIT_Nordic_Test.rData")
```

## Tables for classification

```{r runMode}
BTGINTT4 %>% 
  transmute(CNTRY,predicted=apply(predictedTrain,2,mean)>=0.5) %>%
  table
BTGINTT4 %>% 
  transmute(CNTRY,predicted=apply(predictedTrain,2,mean)>=ROCIT_NordicTr$optimal[4]) %>%
  table

Test %>% 
  transmute(CNTRY,predicted=apply(predictedTest,2,mean)>=ROCIT_Nordic$optimal[4]) %>% 
  table
Test %>% 
  transmute(CNTRY,predicted=apply(predictedTest,2,mean)>=0.5) %>% 
  table
```

## Tables for classification

```{r runMode32, fig.height=9}
BTGINTT4 %>% 
  mutate(predicted = apply(predictedTrain,2,mean),
         Nordic=factor(Nordic,1:0,c("Nordic","Non-Nordic")) ) %>% 
  group_by(CNTRY,Nordic) %>% 
  summarize(Unwg_pred=mean(predicted          >=ROCIT_NordicTr$optimal[4]),
            Wgt_pred =weighted.mean(predicted >=ROCIT_NordicTr$optimal[4],unlabelled(TCHWGT)) ,
            .groups="drop") %>% 
  ggplot(aes(y=CNTRY,color=Nordic))+
    geom_point(aes(x=Unwg_pred,shape="Unweighted"))+
    geom_point(aes(x=Wgt_pred,shape="Weighted"))+
    labs(x="Percentage of teachers predicted to be Nordic",title="Training")

Test %>% 
  mutate(predicted = apply(predictedTest,2,mean),
         Nordic=factor(Nordic,1:0,c("Nordic","Non-Nordic")) ) %>% 
  group_by(CNTRY,Nordic) %>% 
  summarize(Unwg_pred=mean(predicted>=ROCIT_Nordic$optimal[4]),
            Wgt_pred =weighted.mean(predicted>=ROCIT_Nordic$optimal[4],unlabelled(TCHWGT)) ,
            .groups="drop") %>% 
  ggplot(aes(y=CNTRY,color=Nordic))+
    geom_point(aes(x=Unwg_pred,shape="Unweighted"))+
    geom_point(aes(x=Wgt_pred,shape="Weighted"))+
    labs(x="Percentage of teachers predicted to be Nordic",title="Test")
```

## Accuracy in Training data

```{r}
BTGINTT4 %>% transmute(CNTRY,predicted=ifelse(apply(predictedTrain,2,mean) >0.0871,"Nordic","Non") ) %>% 
  table %>% as.data.frame %>% 
  mutate(CNTRY=ifelse(CNTRY %in% c("DNK","NOR","SWE","FIN","ISL"),"Nordic","Non") ) %>% 
  group_by(predicted,CNTRY) %>% 
  summarize(Freq=sum(Freq) , .groups="drop") %>% 
  with(
    data.frame(TruePos =Freq[predicted=="Nordic" & CNTRY=="Nordic"]/sum(Freq[CNTRY=="Nordic"]),
               FalsePos=Freq[predicted!="Nordic" & CNTRY=="Nordic"]/sum(Freq[CNTRY=="Nordic"]),
               TrueNeg =Freq[predicted!="Nordic" & CNTRY!="Nordic"]/sum(Freq[CNTRY!="Nordic"]),
               FalseNeg=Freq[predicted=="Nordic" & CNTRY!="Nordic"]/sum(Freq[CNTRY!="Nordic"])
               )
  )
```

## Accuracy in Test data

```{r}
Test %>% transmute(CNTRY,predicted=ifelse(apply(predictedTest,2,mean) >0.086,"Nordic","Non") ) %>% 
  table %>% as.data.frame %>% 
  mutate(CNTRY=ifelse(CNTRY %in% c("DNK","NOR","SWE","FIN","ISL"),"Nordic","Non") ) %>% 
  group_by(predicted,CNTRY) %>% 
  summarize(Freq=sum(Freq) , .groups="drop") %>% 
  with(
    data.frame(TruePos =Freq[predicted=="Nordic" & CNTRY=="Nordic"]/sum(Freq[CNTRY=="Nordic"]),
               FalsePos=Freq[predicted!="Nordic" & CNTRY=="Nordic"]/sum(Freq[CNTRY=="Nordic"]),
               TrueNeg =Freq[predicted!="Nordic" & CNTRY!="Nordic"]/sum(Freq[CNTRY!="Nordic"]),
               FalseNeg=Freq[predicted=="Nordic" & CNTRY!="Nordic"]/sum(Freq[CNTRY!="Nordic"])
               )
  )
```


```{r}
sessionInfo()
```